Seshadri constants of curve configurations on surfaces

### 2024-03-18 sc-curve-config.tex
Changes by Krishna-18th March (8:35)

\address{UM-DAE Centre for Excellence in Basic Sciences
"Nalanda", Opp Nano Sciences Building,
University of Mumbai, Vidyanagari,
Mumbai 400098, India.}

@@

For a fixed $\alpha \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$, the hyperplane section $X \cap V(x_0 - \alpha x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
given by  
$x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta_j x_3$
for  $1\leq j \leq 4$. Consequiently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. The 48 lines in $\mathcal{L}$ can be partitioned into sets of 4 lines each such that the sum of the four lines in each set is 
linearly equivalent to $\mathcal{O}_X(1)$.

@@

		We now compute the multi-point Seshadri constant of $\mathcal{O}_X(1)$ at the singular locus of 
		the arrangement $\mathcal{L}$.  This arrangement has 216 singular points. So we have 
		$$\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) \le \sqrt{\frac{4}{216}} \sim 0.136.$$
In fact, we claim that
		\[
		\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) = \frac{1}{10}.
		\]
Note that each line $l_{\alpha_i,\beta_j}$ has degree 1 in $\mathbb{P}^3$. So,  from the above discussion, it is clear that 
		\[
		\frac{\mathcal{O}_X(1)\cdot l_{\alpha_i,\beta_j}}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]
		Now let $C \subset X$ be any reduced and irreducible curve such that $C \notin \mathcal{L}$ and which passes through some point in the singular locus of 
		$\mathcal{L}$. By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$

We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore we get
               \begin{eqnarray*}
                \sum\limits_{i=1}^{48} 2 C \cdot l_i &\ge& \sum\limits_{i=1}^{48} 2\left( \sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right) \\
                \Rightarrow  \sum\limits_{i=1}^{24} C \cdot \mathcal{O}_X(1) &\ge&  2\left( \sum\limits_{i=1}^{48}\sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).
               \end{eqnarray*}

>>>>

\address{UM-DAE Centre for Excellence in Basic Sciences, University of Mumbai Santacruz, Mumbai 400098, India}

@@

%For a fixed $\alpha \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$,

The hyperplane section $X \cap V(x_0 - \zeta x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
given by  
$x_0 = \zeta x_1 \; \text{and} \; x_2 = \beta_j x_3$
for  $1\leq j \leq 4$. Consequently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. Similarly, the sum of the four lines 
$x_0 = \alpha_i x_1 \; \text{and} \; x_2 = \zeta x_3$ is linearly equivalent to $\mathcal{O}_X(1)$. Thus we note that the line 
$x_0 = \zeta x_1 \; \text{and} \; x_2 = \zeta x_3$ is in two different sets of 4 lines each so that the sum of lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
Using a similar argument, one can see that there are 24 sets of 4 lines each such that each line in $\mathcal{L}$ appears in \textit{exactly} two of the sets and the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.

%The 48 lines in $\mathcal{L}$ can be partitioned into sets of 4 lines each such that the sum of the four lines in each set is  linearly equivalent to $\mathcal{O}_X(1)$.

@@

		We now compute the multi-point Seshadri constant of $\mathcal{O}_X(1)$ at the singular locus of 
		the arrangement $\mathcal{L}$.  This arrangement has 216 singular points. So we have 
		$$\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) \le \sqrt{\frac{4}{216}} \sim 0.136.$$
In fact, we claim that
		\[
		\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) = \frac{1}{10}.
		\]

Note that each line $l$ in $\mathcal{L}$ has degree 1 in $\mathbb{P}^3$. From the above discussion, for every line $l \in \mathcal{L}$ it is clear that
		\[
		\frac{\mathcal{O}_X(1)\cdot l}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]

		Now let $C \subset X$ be any reduced and irreducible curve such that $C \notin \mathcal{L}$ and which passes through some point in the singular locus of 
		$\mathcal{L}$. We will show that the Seshadri ratio given by $C$ is strictly bigger than $\frac{1}{10}$.

  By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$

We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.  Therefore we get
               \begin{eqnarray*}
                \sum\limits_{i=1}^{48} 2 C \cdot l_i &\ge& \sum\limits_{i=1}^{48} 2\left( \sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right) \\
                \Rightarrow  \sum\limits_{i=1}^{24} C \cdot \mathcal{O}_X(1) &\ge&  2\left( \sum\limits_{i=1}^{48}\sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).
               \end{eqnarray*}
